Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-08-26 ms.tex
added more description of the BOSZ model exploration.

In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

@@

The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.

@@

\subsection{Independent Reduction}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
The K Masuda reduction masks all telluric emission features and any outliers, producing cleaner spectra.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it can be compared to the measurements without convolving the Subaru spectra.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.

@@

We tweak the resolution of the convolution kernel used with the models slightly to obtain a final resolution of 55,000.
Also, we average ll available spectra from the Masuda reduction to increate the signal to noise.
The median spectrum with tweaked Gaussian kernel on the models if visible in Figure \ref{fig:mgTripletBOSZMedian}.
The small difference visible between the median spectrum and the single spectrum is caused by the normalization process, but the lines appear at the same strength.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZMedian}
\end{centering}
\end{figure}

As before, we also compare the data to a BOSZ model with T=5000 K and log(g)=4.5, shown in Figure \ref{fig:mgTripletBOSZMedianW5000}.
The line ratios appear to match the BOSZ model with T=4500 K much better.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Example spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to a 4500 K BOSZ and a 5000 K BOSZ model.}\label{fig:mgTripletBOSZMedianW5000}
\end{centering}
\end{figure}

This motivates a check on the temperatures, so we compare 3 models all with log(g)=4.5 and

@@

\subsection{BOSZ Model Exploration}

We also convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M].

>>>>

In one independent analysis (E Schlawin), we we follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD (red and blue sides) separately.

@@

The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.
In figure \ref{fig:CaILine} we zoom in on the Ca I 6162 $\AA$ feature.
Again, there is no clear match to either BOSZ model.

@@

\subsection{Independent Reduction}
K Masuda independently reduced the \shStar\ Subaru data to examine if there could be an orbiting body on a highly eccentric star-grazing orbit that would reveal itself through radial velocity variations.
This more sophisticated reduction masks all telluric emission features and any outliers, producing cleaner spectra.
Time-variable outliers like cosmic rays are removed by measuring deviations from the median spectrum for the night.
The night-sky emissions from OH and O$_2$ are removed by using the \citet{osterbrock1996lineAtlas} night sky atlas.
All OH and O$_2$ lines are removed regardless if they are visible in the spectrum of \shStar.
Also, we found the median spectrum for the night (2015-05-11) to increase the signal to noise and perform outlier rejection.
The median spectrum is visible in Figure \ref{fig:mgTripletBOSZ}.

\subsection{Comparison to BOSZ}
The BOSZ  \citep{bohlin2017bosz} model database is calculated up to $R = 300,000$ so it should be comparable to measurements without smoothing the Subaru spectra as was necessary for the HIGHRES models above.
We start by comparing R=100,000 models with the measured spectrum of \shStar\ near the Mg triplet, shown in Figure \ref{fig:mgTripletBOSZ}.
The models are convolved with a Gaussian that has a standard deviation $\sigma_G = \lambda/57700$  to obtain a resolution of 50,000.

@@

The BOSZ models appear much smoother than the measured spectrum, even if we use them at the full R=100,000.
\textbf{Perhaps the micro-turbulent velocity (2 km/s) for all models is too high?}
In order for us to compare the BOSZ models and our data, we have to convolve the Subaru spectrum.
They match best if we convolve the data with a R=40,000 kernel so that we could compare the data to the BOSZ models.
Then, we explore the 5 parameters in the BOSZ models: T$_{eff}$, log(g), [M/H], [$\alpha$/M] and [C/M] to constrain these parameters in \shStar.
For each parameter, we change the models by about 2 steps in the BOSZ grid.
For a quantitative measure of the goodness-of-fit, we calculate a $\chi^2$ over the Mg triplet lines from 5160 to 5190 $\AA$.
The errors are estimated from the standard deviation of the spectra over the night.

The sensitivity to each parameter for the BOSZ models are shown in Figure \ref{fig:boszModelParamsMedianSpec}.
A temperature near 4500 K, log(g) = 4.0-4.5, high metallicity ([M/H] $\approx$ 0.5), low $\alpha$ enrichment ($\alpha \approx -0.25$ and solar Carbon to metals ([C/M] $\approx$ 0) are favored by the models.

@@
